\begin{rubric}{Grants and Funding}
%\entry*[\emph{not funded}]%
%    ``Emergent Land Surface Benchmarks for Climate Models,'' 
%    \par Google Research: Creating ML Benchmarks for Climate Problems. 
%    \par First Author: \textbf{DJ Short Gianotti}, PI: D Entekhabi. \$262,172.
%
\entry*[\emph{in prep}]
    \begin{hangparas}{1em}{1}
        \par ``Separating the Structural and Physiological Dynamics of Global Primary Productivity,'' 
        \par NASA Research Opportunities in Earth and Space Sciences, 
        NNH24ZDA001N-CARBON, Carbon Cycle Science.
        \par To be submitted February 17, 2025.
        \par PI: \textbf{DJ Short Gianotti}, CO-Is: BE Morgan, D Entekhabi, DL Des Marais. \~\$750,000.
    \end{hangparas}
% 
\entry*[\multirow{2}{2cm}{\raggedleft \textbf{Funded:} 2024-2027}]
    \begin{hangparas}{1em}{1}
        \par ``Causes of Historical Change, Environmental Resiliency and Future of the Caspian Sea,'' 
        \par Private Donor Grant. 
        \par PI: D Entekhabi, CO-Is: \textbf{DJ Short Gianotti}, MR Alizadeh. \$494,747.
    \end{hangparas}
%
\entry*[\multirow{2}{2cm}{\raggedleft \textbf{Funded:} 2024-2025}]
%\entry*[\textbf{Funded:}\\ 2024-2025]
    \begin{hangparas}{1em}{1}
        \par ``Global Mapping of Groundwater Recharge and Sustainable Aquifer Water Withdrawals Using Satellite Observations,'' 
        \par MIT Climate and Sustainability Consortium. 
        \par First Author: MR Alizadeh, PI: D Entekhabi, CO-I: \textbf{DJ Short Gianotti}. \$122,080.
    \end{hangparas}
%
\entry*[\multirow{2}{2cm}{\raggedleft \textbf{Funded:} 2024-2026}]
    \begin{hangparas}{1em}{1} 
        \par ``Landcover Stability: Heating and Drying of Plants and Soils,'' 
        \par MIT-Portugal Program. 
        \par First Author: \textbf{DJ Short Gianotti}, PI: D Entekhabi. \$259,002.
    \end{hangparas}
%
\entry*[\multirow{2}{2cm}{\raggedleft \textbf{Funded:} 2020-2021}]
        \begin{hangparas}{1em}{1}
            \par ``Analysis of Water Relations in the Soil-Plant Continuum Using Microwave-Lidar Synergy,'' 
            \par Fundaci\'{o} La Caixa \& Massachusetts Institute of Technology, 
            \par PIs: D Chaparro \& D Entekhabi, CO-Is: \textbf{DJ Short Gianotti}, AF Feldman, \& T Jagdhuber. \euro{22,000}, Grant Number 1673204776.
        \end{hangparas}
%
\end{rubric}
